Water Management

### 2020-02-24 Paper/paper.tex
fix figures

@@

\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-opt-irrigation-over-time-evap-inactive.eps}
	\caption{Without Evaporation}
	\label{fig:rainfall-real-data}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-opt-irrigation-over-time-evap-active.eps}
	\caption{With Evaporation}
	\label{fig:value-function}
\end{subfigure}
\caption{Comparison of water level, irrigation amount, rainfall and evaporation over time using real data}
\label{fig:without-vs-with-evaporation}
\end{figure}

@@

%TODO make the figure better
\begin{figure}[ht]
\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-evap-factors-water-levels.eps}
	\caption{Water Level}
	\label{fig:rainfall-real-data}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-evap-factors-utilities.eps}
	\caption{Total Utility}
	\label{fig:value-function}
\end{subfigure}
\caption{Water level and log-scaled total utility over time, scaling evaporation with factors $0, 1, 2, 2.3$ (from top to bottom)}
\label{fig:evaporation-factors}
\end{figure}
%\clearpage

@@

The real rainfall distribution (Figure 11 a) looked quite a bit different then our lognormal distribution with $\mu=0$ and $\sigma=1$.

@@

The higher expected value of rain in the real distribution leads to the optimal irrigation policy showing a higher amount of water used for irrigation at higher water levels (Figure 11 b).

>>>>

\caption{Using Real Data for Rainfall}
\label{fig:real-data}

@@

\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-opt-irrigation-over-time-evap-inactive.eps}
	\caption{Without Evaporation}
	\label{fig:water-level-wo-evap}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-opt-irrigation-over-time-evap-active.eps}
	\caption{With Evaporation}
	\label{fig:total-utility-wo-evap}
\end{subfigure}
\caption{Comparison of water level, irrigation amount, rainfall and evaporation over time using real data}
\label{fig:without-vs-with-evaporation}
\end{figure}

@@

%TODO make the figure better
\begin{figure}[ht]
\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-evap-factors-water-levels.eps}
	\caption{Water Level}
	\label{fig:water-level-evap}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-evap-factors-utilities.eps}
	\caption{Total Utility}
	\label{fig:total-utility-evap}
\end{subfigure}
\caption{Water level and log-scaled total utility over time, scaling evaporation with factors $0, 1, 2, 2.3$ (from top to bottom)}
\label{fig:evaporation-factors}
\end{figure}
%\clearpage

@@

The real rainfall distribution (\ref{fig:rainfall-real-data}) looked quite a bit different then our lognormal distribution with $\mu=0$ and $\sigma=1$.

@@

The higher expected value of rain in the real distribution leads to the optimal irrigation policy showing a higher amount of water used for irrigation at higher water levels (\ref{fig:optimalIrrigationPolicy-real-data}).
